---
title: "Cleans Miller-ter Kuile Body Size data"
author: "Camila Vargas"
date: "8/12/2021"
output: html_document
---

This script cleans data on Body sizes for taxa including cane spiders, geckos, and other spiders and insects provided by Ana Miller-ter Kuile.

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(googledrive)
library(here)
library(data.table)
library(tidyverse)
library(readxl)
library(janitor)
library(lubridate)

## Sets R not to use scientific notations
options(scipen=999) 

# Create raw data folders - DO I NEED A IF STATEMENT???

if (!dir.exists(here::here("/raw_data"))){
  dir.create(paste0(getwd(),"/raw_data"))
}

## If necesary create a sub directory inside the raw_data. This will be the case for porject that will end up in more than one package.
dir.create(paste0(getwd(),"/raw_data/mtk_body_size"))

```



## Download data files into local computer

In this case, the project has multiple types of data. Each type of data will be cleaned in its own Rmd and will become its own package. 
Make sure the file path on the code is updated to the correct folder. In this case we are working with the weather data, so data is saved inside the `weather` folder. Update folder name if you are downloading other type of data.

```{r download files}
# url of folder where the data lives
# Copy pasete the url of the folder where the data lives

folder_url <- "https://drive.google.com/drive/u/1/folders/1Ypg74d5XzyCLG03qEVR1eaJOrvREyRHC"

# list of files inside the folder
files <- drive_ls(as_id(folder_url))

## Download each file to local computer
purrr::walk2(
    map(files$id, as_id),
    paste0("raw_data/mtk_body_size/", files$name),
    drive_download,
    overwrite = TRUE)

# Check all files where downloaded
# Count files inside the raw_data forder to make sure the number of files downloaded is what is expected.
raw_data_path <- paste0(getwd(), "/raw_data/mtk_body_size")

length(list.files(raw_data_path))

```



## Functions and tables with files info
Creating a table with all of our files by type to use as an index to access each file.

```{r read data}

## List wit all csv files in raw data
all_csv <- tibble(list.files(raw_data_path, pattern = ".csv")) %>% 
  rename(file_name = 1) %>% 
  mutate(path = paste0(raw_data_path, "/", file_name),
         n = 1:n(),
         type = "body_size") %>% 
  unite(obj_name, type, n, sep = "_", remove = FALSE)

## List with all xls files
all_xls <- tibble(list.files(raw_data_path, pattern = c("xls", "xlsx"))) %>% 
  rename(file_name = 1) %>% 
  mutate(path = paste0(raw_data_path, "/", file_name),
         n = 1:n(),
         type = "body_size") %>% 
  unite(obj_name, type, n, sep = "_", remove = FALSE)


## function to read csv and clean names as we read the file
read_csv_clean <- function(dataset){
  
  read_csv(dataset) %>% 
    clean_names()
}

## Check sheets in Excels files

excel_sheets(all_xls$path[2])
excel_sheets(all_xls$path[3])
excel_sheets(all_xls$path[4])
excel_sheets(all_xls$path[5])
excel_sheets(all_xls$path[6])
excel_sheets(all_xls$path[7])

```

## Read csv files

The only csv file is Spider Insect mass length

```{r}
## Read in all csv
for (i in all_csv$n){
  
  assign(all_csv$obj_name[i], read_csv_clean(all_csv$path[i]))
}

```


## Read excel files

**Cane Spider**
```{r}
## chseck sheet names
excel_sheets(all_xls$path[1])

cane_spider_09 <- read_excel(all_xls$path[1], sheet = "Sheet1") %>% 
  clean_names()

## Is this table a summary table from data above?
cane_spider_09_2 <- read_excel(all_xls$path[1], sheet = "Sheet2") %>% 
  clean_names()

cane_spider_10 <- read_excel(all_xls$path[2], sheet = "Sheet1") %>% 
  clean_names()


excel_sheets(all_xls$path[6])
cane_spider_15_loc <- read_excel(all_xls$path[6], sheet = "Spider Vial Locations") %>% 
  clean_names()

cane_spider_15_size <- read_excel(all_xls$path[6], sheet = "Spider Sizes") %>% 
  clean_names()

cane_spider_15_me <- read_excel(all_xls$path[6], sheet = "Measurement Errors") %>% 
  clean_names()


```

**Gecko**
```{r}
excel_sheets(all_xls$path[3])
gecko_10 <- read_excel(all_xls$path[3], sheet = "Sheet1") %>% 
  clean_names()

excel_sheets(all_xls$path[4])
gecko_11 <- read_excel(all_xls$path[4], sheet = "geckos", skip = 1) %>% 
  clean_names()

excel_sheets(all_xls$path[4])
gecko_11_summary <- read_excel(all_xls$path[4], sheet = "survey summary", skip = 1) %>% 
  clean_names()

excel_sheets(all_xls$path[5])
gecko_14 <- read_excel(all_xls$path[5], sheet = "geckos", skip = 1) %>% 
  clean_names()

gecko_14_summary <- read_excel(all_xls$path[5], sheet = "survey summary", skip = 1) %>% 
  clean_names()

excel_sheets(all_xls$path[7])
gecko_15_surv <- read_excel(all_xls$path[7], sheet = "Survey Data") %>% 
  clean_names()

gecko_15_me <- read_excel(all_xls$path[7], sheet = "Gecko Measurements") %>% 
  clean_names()


```

